Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-12 document/ms.tex
descriptions of synthetic catalogs

@@

In order to get a feeling for the constraints provided by our method and to
explore any biases introduced by ignoring the observational uncertainties, we
start by ``observing'' a few synthetic catalogs from qualitatively different
known occurence rate functions.
For each of these simulations, we'll take the completeness function computed
by \citet{petigura} as given.
In general, \eq{poisson-like} can be sampled using a procedure called thinning
(\citealt{poisson}) but for our purposes, we'll simply consider a piecewise
constant rate function evaluated on a fine grid in (log-) period and radius.
For this discrete function, the generative procedure is simply:
\begin{enumerate}
{\item loop over each grid cell $i$,}
{\item draw Poisson random integer $K_i\sim\mathrm{Poissson}(\obs{\rate}_i)$
with the observable rate evaluated in the cell, and}
{\item distribute $K_i$ catalog entries in the cell randomly.}
\end{enumerate}
We then choose fractional observational uncertainties on the radii from the
\citet{petigura} catalog and apply them to the catalog assuming that they are
Gaussian.

>>>>

\dfmtodo{Talk about how we apply the geometric transit probability.}

@@

In order to get a feeling for the constraints provided by our method and to
explore any biases introduced by ignoring the observational uncertainties, we
start by ``observing'' a few synthetic catalogs from qualitatively different
known occurence rate functions.
For each of these simulations, we'll take the completeness function computed
by \citet{petigura} as given.
In general, \eq{poisson-like} can be sampled using a procedure called thinning
(\citealt{poisson}) but for our purposes, we'll simply consider a piecewise
constant rate function evaluated on a fine grid in log-period and log-radius.
For this discrete function, the generative procedure is simple;
\begin{enumerate}
{\item loop over each grid cell $i$,}
{\item draw Poisson random integer $K_i\sim\mathrm{Poissson}(\obs{\rate}_i)$
with the observable rate evaluated in the cell, and}
{\item distribute $K_i$ catalog entries in the cell randomly.}
\end{enumerate}
We then choose fractional observational uncertainties on the radii from the
\citet{petigura} catalog and apply them to the true catalog as Gaussian noise.

We generate synthetic catalogs from two qualitatively different rate
functions.
Both distributions are generated by a separable model
\begin{eqnarray}
\rate_\ratepars (\ln\period,\,\ln\radius) &=&
    \rate_\ratepars^{(\period)}(\ln\period)\,
    \rate_\ratepars^{(\radius)}(\ln\radius)
\end{eqnarray}
but fit using the full general model.
The first model has a smooth occurence surface where both distributions are
smooth broken power laws.
The second is designed to be exactly the distribution inferred by
\citet{petigura} in the range that they considered and then smoothly
extrapolated outside that range.

For each catalog, we directly applied the inverse-detection-efficiency
procedure as implemented by \citealt{petigura}\footnote{our implementation
exactly reproduces their results when applied to the published catalog} and
our probabilistic method.
